---
title:  "<br> London Labour Market Update"
date: "[Matthew Tibbles](mailto:matthew.tibbles@london.gov.uk), `r format(Sys.Date(),'%B %Y')`"
runtime: shiny
output:
  html_document:
    toc: true
    toc_float: true
    css:  !expr "here::here('FORMATTING','GLAstyle.css')"
    includes:
      in_header: !expr "here::here('FORMATTING','favicon.html')"
      before_body: !expr "here::here('FORMATTING','header.html')"
      after_body: !expr "here::here('FORMATTING','footer.html')"
---

```{r setup, include=FALSE}
  
  knitr::opts_chunk$set(echo = TRUE,scipen=999)
  knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
  options("scipen"=100, "digits"=4)
  


  
```

```{r, include=F}
library(here)
library(shinyglide)
library(shinyjs)
library(bslib)
source(here('scripts/master.R'))


art_choices <- 1:4
art_proxy_list <- lapply(
  art_choices, function(q) {
    #print(q)
    generate_regional_proxy(
      SURVEY_PATH, RELEASE_YEAR,
      list('code'=REGION_QUESTION_LIST[[1]][q],'theme'=REGION_QUESTION_LIST[[2]][q], 'color'=REGION_QUESTION_LIST[[3]][q])
    )
  }
)
useShinyjs()




```

```{js, echo=F}
// JS width changes
// R Markdown is using Bootstrap 3.3.5, see legacy documentation here
// https://getbootstrap.com/docs/3.3/css/#grid

// TOC column
const TOC_col = document.querySelector('div.row>div:not(div+div)');  // First div element under div.row
TOC_col.classList.replace('col-sm-4', 'col-sm-2');  // sm: Change TOC column width from 33% to 17% of total
TOC_col.classList.replace('col-md-3', 'col-md-2');  // md: Change TOC column width from 25% to 17% of total

// Main column
const main_col = document.querySelector('div.row>div+div');  // Second (and last) div element under div.row
main_col.classList.replace('col-sm-8', 'col-sm-10');  // sm: Change main column width from 67% to 83% of total
main_col.classList.replace('col-md-9', 'col-md-10');  // md: Change main column width from 75% to 83% of total
main_col.classList.add('col-sm-offset-2', 'col-md-offset-2')  // sm+md: offset main column by width of TOC (for CSS styling below)
```

```{css, echo=FALSE}
/* CSS width changes */

/* Entire page - make wider, default setting is much too narrow */
/* https://stackoverflow.com/questions/38367392/override-rmarkdown-theme-in-order-to-change-html-page-width/54348996#54348996 */
div.main-container {
  width: 1280px !important;
}
/* TOC column - move to left edge */
/* https://medium.com/@TheAtlasTeam/fixed-width-sidebars-in-bootstrap-6bd83db75669 */
div.row>div:not(div+div) {
  position: fixed;
  left: 0px;
}
/* TOC container within the TOC column - make narrower */
#TOC {
  max-width: 200px !important;
  width: 200px !important;
}
```

<hr  width="100%" style="background-color: rgb(134,139,142);height: 1.0px;margin: 0;"/>
<!-- Summary of findings - MANUALLY ADJUST -->
<br/>

::: {.quotebox .quote_symbol}

Insert
<br><br> 
Some text
<br><br> 
about the 
<br><br> 
participation survey 
<br><br> 


:::


<hr  width="100%" style="background-color: rgb(134,139,142);height: 1.0px;margin: 0;"/>

<br/>

# Arts 
<br/>



```{r, echo=F}
#fluidRow(
  #highchartOutput('art_plot', height='65vh'),
  shinyjs::hidden(uiOutput("art_select_btn"))#,
  highchartOutput('art_plot', height='75vh')
  uiOutput("art_previous_btn")#,
  uiOutput("art_next_btn")
#)



# div(class='glide-screen',
# shinyglide:: glide(
#   screen(
#     navset_card_tab(
#       title='Comparison level',
#       nav_panel(
#         "Regional comparison", align='left',
#         highchartOutput('plot1', height='65vh')
#       )
#     )
#   ),
#   screen(
#     navset_card_tab(
#       title='Comparison level',
#       nav_panel(
#         "Regional comparison", align='left',
#         highchartOutput('plot2', height='65vh')
#       )
#     )
#   )
# )
# )





  
```


```{r, context="server", echo=F}

output$selected <- renderText({
  paste0('You have selected ', input$art_select)
})

output$art_select_btn <- renderUI({
  selectInput(
    inputId="art_select",
    label="Question",
    choices = art_choices,
    selected=1,
    multiple=F,
    selectize=T
  )
})

output$t <- renderUI({textOutput(input$art_select)})

output$art_previous_btn <- renderUI({
  actionButton(
    "art_previous", 
    label = "Previous"
  )
})
output$art_next_btn <- renderUI({
  actionButton(
    "art_next", 
    label = "Next"
  )
})

output$art_plot <- renderHighchart({
  output_list[[1]]
})

observeEvent(input$art_previous, {
  current <- which(art_choices == input$art_select)
  if(current > 1) {
    updateSelectInput(
      session, "art_select",
      selected = art_choices[current - 1]
    )
    
    highchartProxy("art_plot") %>%
    hcpxy_update_series(
      id = "central",
      data=data.frame(art_proxy_list[[as.numeric(input$art_select)-1]][2])$prop_resp
    ) %>%
    hcpxy_update_series(
      id = "confidence",
      data=list_parse2(
        data.frame(
          low=data.frame(art_proxy_list[[as.numeric(input$art_select)-1]][2])$prop_resp_lb,
          high=data.frame(art_proxy_list[[as.numeric(input$art_select)-1]][2])$prop_resp_ub
        )
      )
    ) %>%
    hcpxy_update(
      subtitle = list(text=art_proxy_list[[as.numeric(input$art_select)-1]][1])#,
    #   tooltip = list(
    #     pointFormat = "<span style='font-size:1.6vh; font-weight: normal;'><span    style='color:{point.color}'>\u25CF</span> {point.name}</span><br>Central estimate: <b>{point.prop_resp}%</b><br>Lower-Upper estimate: <b>{point.prop_resp_lb}% - {point.prop_resp_ub}%</b>"
    # ) 
    ) 

    # hcpxy_update_series(
    #   id = "confidence",
    #   data=list(
    #     low=data.frame(art_proxy_list[[as.numeric(input$art_select)]][2])$prop_resp_lb,
    #     high=data.frame(art_proxy_list[[as.numeric(input$art_select)]][2])$prop_resp_ub
    #   )
    # hcpxy_set_data(
    #   type='bar',
    #   data=data.frame(art_proxy_list[[as.numeric(input$art_select)]][2]),
    #   mapping = hcaes(x = region, y = round(prop_resp,1), color=color),
    #   redraw = FALSE,
    #   animation = list(enabled=T),
    #   updatePoints = TRUE
    # ) %>%
    # hcpxy_set_data(
    #   type='errorbar',
    #   data=data.frame(art_proxy_list[[as.numeric(input$art_select)]][2]),
    #   mapping = hcaes(x=region, low=prop_resp_lb, high=prop_resp_ub),
    #   redraw = FALSE,
    #   animation = list(enabled=T),
    #   updatePoints = TRUE
    # ) 
      #hcaes(x = region, y = round(prop_resp,1), color=color)
      #hcaes(x = region, y = round(prop_resp,1), color=color)
    #)
    # hcpxy_update_series(
    #   id = "confidence",
    #   data=art_proxy_list[[as.numeric(input$art_select)]][2], 
    #   hcaes(x=region, low=prop_resp_lb, high=prop_resp_ub)
    # ) 
    
  }
}, ignoreNULL = T, ignoreInit = F)

observeEvent(input$art_next, {
  current <- which(art_choices == input$art_select)
  if(current < length(art_choices)){
    updateSelectInput(
      session, "art_select",
      selected = art_choices[current + 1]
    )
    
    highchartProxy("art_plot") %>%
    hcpxy_update_series(
      id = "central",
      data=data.frame(art_proxy_list[[as.numeric(input$art_select)+1]][2])$prop_resp
    ) %>%
    hcpxy_update_series(
      id = "confidence",
      data=list_parse(
        data.frame(
          low=data.frame(art_proxy_list[[as.numeric(input$art_select)+1]][2])$prop_resp_lb,
          high=data.frame(art_proxy_list[[as.numeric(input$art_select)+1]][2])$prop_resp_ub
        )
      )
    ) %>%
    hcpxy_update(
      subtitle = list(text=art_proxy_list[[as.numeric(input$art_select)+1]][1])#,
    #   tooltip = list(
    #     valueSuffix= '%',
    #     borderWidth=2.6,
    #     style=list(fontSize='1.35vh'),
    #     shape='callout',
    #     useHTML = TRUE,
    #     headerFormat = "",
    #     pointFormat = "<span style='font-size:1.6vh; font-weight: normal;'><span    style='color:{point.color}'>\u25CF</span> {point.name}</span><br>Central estimate: <b>{point.prop_resp}%</b><br>Lower-Upper estimate: <b>{point.prop_resp_lb}% - {point.prop_resp_ub}%</b>"
    # ) 
    )
 #%>%
    # hcpxy_update_series(
    #   id = "confidence",
    #   data=list(
    #     low=data.frame(art_proxy_list[[as.numeric(input$art_select)]][2])$prop_resp_lb,
    #     high=data.frame(art_proxy_list[[as.numeric(input$art_select)]][2])$prop_resp_ub
    #   )
    #)
    # hcpxy_set_data(
    #   type='bar',
    #   data=data.frame(art_proxy_list[[as.numeric(input$art_select)]][2]),
    #   mapping = hcaes(x = region, y = round(prop_resp,1), color=color),
    #   redraw = FALSE,
    #   animation = list(enabled=T),
    #   updatePoints = TRUE
    # ) %>%
    # hcpxy_set_data(
    #   type='errorbar',
    #   data=data.frame(art_proxy_list[[as.numeric(input$art_select)]][2]),
    #   mapping = hcaes(x=region, low=prop_resp_lb, high=prop_resp_ub),
    #   redraw = FALSE,
    #   animation = list(enabled=T),
    #   updatePoints = TRUE
    # ) 
    # %>%
    # hcpxy_update_series(
    #   id = "confidence",
    #   data=art_proxy_list[[as.numeric(input$art_select)]][2], 
    #   hcaes(x=region, low=prop_resp_lb, high=prop_resp_ub)
    # ) 
  }
}, ignoreNULL = T, ignoreInit = F)





```


<a href="#top">Back to top</a>

<hr  width="100%" style="background-color: rgb(134,139,142);height: 1.0px;margin: 0;"/>

<br/>



<hr  width="100%" style="background-color: rgb(134,139,142);height: 1.0px;margin: 0;"/>

<br/>

### Change on previous year, regions

<a href="#top">Back to top</a>

<hr  width="100%" style="background-color: rgb(134,139,142);height: 1.0px;margin: 0;"/>

<br/>

more 
### more

### even more

### even more of more


# Measuring the labour market

<br/>

The ONS has published its latest [labour market update](https://www.ons.gov.uk/employmentandlabourmarket/peopleinwork/employmentandemployeetypes) covering Labour Force Survey (LFS) data for the three months ending  and real-time information (RTI) data up to This bulletin presents the latest headline labour market estimates for London.

Please note:

-   Many of the statistics presented here are estimates based on surveys, and as such have a margin of error -- known as sampling variability.

-   They also cover different reference periods or count dates.

More information and previous GLA Economics analyses can be found on our labour market analysis [page](https://data.london.gov.uk/dataset/gla-economics-covid-19-labour-market-analysis).

More information on the data used and a glossary of terms can be found on the [ONS website](https://www.ons.gov.uk/employmentandlabourmarket/peopleinwork/employmentandemployeetypes/methodologies/aguidetolabourmarketstatistics).

<a href="#top">Back to top</a>


</font>

::: {.tocify-extend-page data-unique="tocify-extend-page" style="height: 0;"}
:::
